### 2020-05-17 writeup/proof_transfer_ex.tex
sec 3.2
sec 3.3

\subsection{Proof of Proposition \ref{prop_data_size}}

@@

\subsection{Proof of ???}
Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.

@@

\medskip

>>>>

\subsection{Proof of Proposition \ref{prop_data_size}}\label{app_proof_data}

@@

\subsection{Proofs of Proposition \ref{prop_covariate}}

	We have that the test error satisfies
\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
where $\lambda_p$ is the smallest singular value of $p$ and
$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.

\begin{proof}
From equation \eqref{eq_a2}, we get
$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
With these two bounds, we can easily conclude \eqref{approxteM}.

For the second statement, we find that we need to minimize
$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
\end{proof}

\iffalse
Note that for the case of $k$ tasks with the same covariates, since there is no covariate shift and the data ratio is always equal to one, the main factor is model distance.

@@

\medskip
\fi

### 2020-05-17 writeup/transfer.tex
sec 3.2
sec 3.3

\subsection{Covariance Alignment}

Now we apply Theorem \ref{thm_cov_shift} to show how covariate shift affects the rate of transfer.

@@

We can extend the above observation for Example \ref{example comple} to more general cases with arbitrary covariate shift. To compare different choices of $M$, we need to fix a scaling for them, because otherwise $aM$ always achieves a smaller error than $M$ for $a>1$. For this purpose, we introduce the following condition
\be\label{GMcons}\det(M^\top M)= a^p \Leftrightarrow \prod_{i=1}^p \lambda_i = a^p\ee
for some constant $a>0$, and compare different choices of $M$ under this constraint. The next proposition shows that, roughly speaking, as long as there are sufficiently many source task datas, then $M=a\id$ always gives (approximately) the smallest test error.
\begin{proposition}
We have that the test error satisfies
\be\label{approxteM}  te(M)\left(1 -  \frac{n_2}{n_1-p} \frac{1}{\lambda_p^2 + \frac{n_2}{n_1-p}}\right)  \le  \frac{\sigma^2}{n_1+n_2}\tr\left( \frac{1}{a_1M^\top M + a_2}\right) \le te(M),\ee
where $\lambda_p$ is the smallest singular value of $p$ and
$$te(M):= \frac{\sigma^2}{a_1(n_1+n_2)}\tr\left( \frac{1}{M^\top M}\right) .$$
Moreover, for all $M$ satisfying \eqref{GMcons}, the minimum of $te(M)$ is attained when $M= a\id$.
\end{proposition}
\begin{proof}
From equation \eqref{eq_a2}, we get
$$a_1\ge \frac{n_1-p}{n_1+n_2},\quad a_2\le \frac{n_2}{n_1+n_2}.$$
With these two bounds, we can easily conclude \eqref{approxteM}.

For the second statement, we find that we need to minimize
$$\tr\left( \frac{1}{M^\top M}\right) = \sum_{i=1}^p\frac{1}{\lambda_i},\quad \text{under}\ \ \prod_{i=1}^p\lambda_i=a^p.$$
Then using AM-GM inequality, we conclude that the sum $\sum_{i=1}^p\lambda_i^{-1}$ is smallest when $\lambda_1=\cdots=\lambda_p = a$.
\end{proof}

>>>>

\subsection{Covariate Shift}

So far we have considered settings where $\Sigma_1 = \Sigma_2$.
This setting is relevant for multi-class image classification settings, where different tasks share the same input features.
In general, the covariance matrices of the two tasks may be different, e.g. in text classification.
In this part, we use our tools to provide a case study on the effect of applying multi-task learning for two tasks when $\Sigma_1 \neq \Sigma_2$.

For this setting, covariate shift is captured by the matrix $M = \Sigma_1^{1/2} \Sigma_2^{-1/2}$.
We ask: is it better to have $M$ as being close to identity, or should $M$ involve varying levels of singular values?
Understanding this question has implications for applying normalization methods in multi-task learning \cite{LV19,CBLR18,YKGLHF20}.
Our result shows that if $n_1$ is much larger than $n_2$, then the optimal $M$ matrix is equal to identity, under certain assumptions on its range of singular values (to be formulated in Proposition \ref{prop_covariate}).
On the other hand, if $n_1$ is comparable or even smaller than $n_2$, we show an example where having ``complementary'' covariance matrices is better performing than having the same covariance matrices.

\begin{example}
	To compare different choices of $M$ on the performance of $\hat{\beta}_t^{\MTL}$, we assume an upper bound on the scale of $M$.
	%, because otherwise $aM$ always achieves a smaller error than $M$ for $a>1$. For this purpose, we introduce the following condition
	Consider the following family of matrices
	\begin{align*}
		\cS_{\mu}\define\bigset{M \mid \det\bigbrace{\frac{1}{p}M^\top M} \le \mu}.
	\end{align*}
	We assume that $\beta_2$ has i.i.d. entries with mean zero and variance $\kappa^2$ and $\beta_1 - \beta_2$ has i.i.d. entries with mean $0$ and variance $d^2$.
%	for some constant $a>0$, and compare different choices of $M$ under this constraint. The next proposition shows that, roughly speaking, as long as there are sufficiently many source task datas, then $M=a\id$ always gives (approximately) the smallest test error.
	The following proposition shows that when $n_1$ is large enough compared to $n_2$, $\te(\hat{\beta}^{\MTL})$ is minimized within the family of $\cS_{\mu}$ when $M = \mu\id$.
\end{example}

\begin{proposition}\label{prop_covariate}
	In the setting of Example \ref{ex_basic}, assume that $c_1 > ??$.
	As a parameter of $M \in \cS_{\mu}$, we have that $\te(\hat{\beta}_t^{\MTL})$ is minimized when $M = \mu\id$.
\end{proposition}

@@
